\documentclass[11pt,a4paper,sans]{moderncv}

%-------------------- STYLE & COLOR --------------------
\moderncvstyle{banking}
\moderncvcolor{blue}
\nopagenumbers{}

%-------------------- PACKAGES --------------------
\usepackage[scale=0.9]{geometry}
\usepackage{fontawesome5}
\usepackage{enumitem}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{qrcode}
\usepackage[hidelinks,unicode,breaklinks=true,bookmarksopen=true]{hyperref}

%-------------------- PERSONAL DATA --------------------
\name{Samuel}{Chapuis}
\title{Aerospace \& Big Data Engineer}
% \address{Ile de France}{}

\phone[mobile]{+33~7~28~55~29~98}
\email{samuel.chapuis@student-cs.fr}
\social[github]{Samuel-Chapuis}
\newcommand{\webcv}{https://del-dynamic.fr/cv-samuel-chapuis.html}

%-------------------- DOCUMENT --------------------
\begin{document}
\makecvtitle

\begin{center}
\small
\href{\webcv}{\webcv}\hspace{1em}\qrcode[height=1.6cm]{\webcv}
\end{center}
\vspace{0.4em}

%------------------------------------------------------
\section{Formation}
\cventry{2025--2026}{MSc Applied Mathematics – Big Data Management and Analytics }{CentraleSupélec – Paris-Saclay}{Saclay, FR}{}{}
\cventry{2025}{Exchange Student – CFD Research Program directed by Prof. Cepeda-Rizo}{CSULB -California State University, Long Beach}{Long Beach, USA}{}{}
\cventry{2021--2026}{French Engineering Degree (MEng equiv.) – Aerospace}{ISAE ESTACA}{SQY, FR}{}{}

%------------------------------------------------------
\section{Expériences professionnelles}
\cventry{since 2024}{Founder \& Service Engineer}{del.dynamic}{Paris, FR}{}{
I created my own company providing engineering design services for industrial partners.
}
\cventry{2026}{Research Internship}{CEA}{Buyere, FR}{}{
Diffusion framework for Rayleigh–Taylor instabilities in two-phase turbulent flows, using wavelet.
}
\cventry{2024--2025}{Research Engineer Internship}{IrisLab}{Saclay, FR}{}{
Development of an autonomous laser emission platform and a photovoltaic receiver for in-flight charging.
}
\cventry{2023}{Internship}{Réunion Aérienne et Spatiale}{Paris, FR}{}{
Data analysis on space missions to evaluate their insurability.
}
% \cventry{2022}{Internship}{Société du Grand Paris}{Paris, FR}{}{
% Data processing in Java and VBA – Site security management.
% }

%------------------------------------------------------
\section{Projets associatifs et techniques}
\cventry{2024--2025}{Dassault Aviation}{Dassault UAV Challenge}{Bordeaux, FR}{}{
Development of a new autonomous flight platform.
}
\cventry{2024--2025}{Planet Science}{Probe Balloon}{Paris, FR}{}{
Design of a high-altitude sounding balloon for upper-atmosphere observation.
}
\cventry{2023--2024}{Dassault Aviation}{Dassault UAV Challenge}{Bordeaux, FR}{}{
Creation of an autonomous wing capable of vertical take-off and mini-UAV deployment.
}
\cventry{2023}{Safran}{Droneload \& UTAC Contests}{Montlhéry, FR}{}{
Design and realization of autonomous vehicles for competition.
}

%------------------------------------------------------
\section{Compétences}
\cvitem{Languages}{\textbf{French:} Native \quad \textbf{English:} Fluent \quad \textbf{Spanish:} B2}
\cvitem{Software Programming}{C, C++, Java, Python}
\cvitem{Web Development}{HTML, CSS, JavaScript}
\cvitem{CAD \& Simulation}{SolidWorks, CATIA, Fusion 360}
\cvitem{Mechatronics}{Raspberry~Pi, Arduino, ESP32, Matlab, KiCad}
\cvitem{CFD \& Thermal}{Matlab, XLRFS, Ansys Fluent, SolidWorks Flow Simulation}

% %------------------------------------------------------
% \section{Liens}
% \cvitem{GitHub}{\href{https://github.com/Samuel-Chapuis}{https://github.com/Samuel-Chapuis}}

\end{document}
